### 2025-05-06 paper/sections/section1-Introduction.tex
Update tex file make it can public

\documentclass[../article.tex]{subfiles} % 继承主文档配置

\begin{document}

% 子文件内容（直接写正文，无需重复导言区）
\section{绪论}
\subsection{研究背景}

XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX

XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX

XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX

XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX

\subsection{研究意义与目的}

XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX

\end{document}