### 2025-05-06 paper/sections/section2-.tex

\documentclass[../article.tex]{subfiles} % 继承主文档配置

\graphicspath{{../../images}} % 设置图片路径

\begin{document}

\section{XXXXXXXXXXX}
\subsection{XXXXXXXXXXX}

XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX

XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX

XXXXXXXXXXXXXXXXXXXX\cite{soft-nms}，\cite{hog}、\cite{vcnn} \cite{solov2}。

\end{document}